### 2015-02-22 fundamentals/examples.tex
cycstub typo

A number of projects and tools outside of the core simulation kernel have been
developed to improve the scope and the diversity of the capabilities in the \Cyclus
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed
under close integration with the \Cyclus kernel.  These tools are used to ease development
and simulation design (Cystub, Cycic, Ciclus), data visualization and analysis (Cyclist, Cyan),
and remote execution (Cloudlus).

>>>>

A number of projects and tools outside of the core simulation kernel have been
developed to improve the scope and the diversity of the capabilities in the
\Cyclus ecosystem. Table \ref{tab:coretools} lists the tools and projects
developed under close integration with the \Cyclus kernel.  These tools are used
to ease development and simulation design (Cycstub, Cycic, Ciclus), data
visualization and analysis (Cyclist, Cyan), and remote execution (Cloudlus).
